\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}

\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{tikz}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{pgfplots}
\usepackage{nccmath}
\usepackage{mathtools}
\usepackage{pgfplots}
\usepackage{mathtools,amssymb}
\usepackage{tikz}
\usepackage{xcolor}
\pgfplotsset{compat = newest}
\author{Chris Camano: ccamano@sfsu.edu}
\title{MATH440 PProblems 1 }
\date{1/30/2022}
% Margins
\topmargin=-0.45in
\evensidemargin=0in
\oddsidemargin=0in
\textwidth=6.5in
\textheight=9.0in
\headsep=0.25in


\begin{document}
\maketitle
\textbf{Problem set: 2,3,7,11,
18, 19, 20, 24, 28,29}
\section{2.2 Practice Problems}\\
\textbf{Problem 2.2.2}\\
 Three dice are tossed, one red, one blue, and one green . What outcomes make up the event A that the sum of the three faces showing equals 5?
\begin{align*}
  A=\{ (1,1,3),(1,2,2),(1,3,1),(2,1,2),(2,2,1),(3,1,1)\}
\end{align*}
\\\\
\textbf{Problem 2.2.3}\\
An urn contains six chips numbered 1 through 6. Three are drawn out. What outcomes are in the vent "Second smallest ship is 3"? Assume order is not relevant.
\begin{align*}
  A=\{(6,3,1),(5,3,1),(4,3,1),(6,3,2),(5,3,2),(4,3,2)\}
\end{align*}
\\\\
\textbf{Problem 2.2.7}\\
Let P be the set of right traingles with a 5" hypotenuse and whose height and length are a and b, respectively. Characterize the outcomes in P.
\begin{align*}
  P=\{(a,b)|a^2+b^2=25,a,b \in \mathbb{R}\}\\
  P=\{(3,4),(4,3)\}
\end{align*}
\\\\
\textbf{Problem 2.2.11}\\
A woman has her purse snatched by two teenagers. She is subsequently shown a police lineup consisting of five suspects, incuding two perpetrators. What is the sample space associated with the experiment: "Woman picks two suspects out of lineup"? Which outcomes are in the event A: She makes at least one incorrect identification?
\begin{align*}
  S=\{(p_1,i_1),(p_1,i_2),(p_1,i_3),(p_2,i_1),(p_2,i_2),(p_2,i_3),(i_1,i_2),(i_1,i_3),(i_2,i_3),(p_1,p_2)\}\\ \textbf{ Where p is perp and i is innocent}\\
  A=\{(p_1,i_1),...,(p_1,i_k),(p_2,i_1),...,(p_1,i_k),(i_1,i_2),(i_1,i_3),(i_2,i_3)\}k\in[2,3]
\end{align*}
\\\\
\textbf{Problem 2.2.18}
Find $A \cap B \cap C$ if $A =\{x|  0 \leq x \leq 4\}, B=\{x|2 \leq x \leq 6 \}, C=\{x| x \in \mathbb{Z}\}$
\begin{align*}
  A=\{0,1,2,3,4\}\\
  B=\{2,3,4,5,6\}\\
  A \cap B =\{2,3,4\}\\
  (A\cap B)\cap C= \{2,3,4\}
\end{align*}
\\\\
\textbf{Problem 2.2.19}
An Electronic system has four components divided into two pairs. The two components of each pair are wired in parallel; the two pairs are wired in series. Let $A_{ij}$ denote the event " ith compontnt in jth pair fails", i = 1,2, j=1,2. Let A be the event System fails write A in terms of the $A_{ij}$s
\begin{align*}
A=(A_{11} \cap A_{21})\cap (A_{12}\cap A_{22})
\end{align*}
\\\\
\textbf{Problem 2.2.20}
Define: $A=\{x|0\leq x \leq 1 \}, B= \{x| 0\leq x \leq 3\},C=\{x| -1 \leq x \leq 2 \}$. Draw Diagrams for each.\\
Tikz Skills still pending:
\\\\
\textbf{Problem 2.2.24}
Let $A_1,A_2,...,A_k$ be any set of events defined on a sample space S. What outcomes belong to the event: \\
\[
  A=(A_1 \cup A_2 \cup ...\cup A_k) \cup (A^C_1 \cap A^C_2 \cap ... \cap A^C_k)
\]
\begin{align*}
  A=(A_1 \cup A_2 \cup ...\cup A_k) \cup (A_1 \cap A_2 \cap ... \cap A_k)^C=S\quadd \textbf{The entire Sample Space}
\end{align*}
\\\\
\textbf{Problem 2.2.28}
Let events A and B and sample S be defined as the following intervals:
\begin{align*}
  S=\{x|0 \leq x \leq 10\}\\
  A=\{x|0<x<5\}\\
  B=\{x|3\leq x \leq 7\}
\end{align*}'
Characterize the following:
\begin{align*}
  A=\{x|0<x<5\}=\{x|1\leq x \leq 4\}\\
  a)A^C\\
  \quadd A^C=\{0,6,7,8,9,10\}\\\\
  b)A \cap B \\
  \quadd A\cap B = \{3,4\}\\\\
  c) A\cup B\\
  \quadd A \cup B =\{ 1,2,3,4,5,6,7\}\\\\
  d) A\cap B^C\\
  \quadd A \cap B^C=\{1,2\}\\\\
  e) A^C \cup B\\
  \quadd A^C \cup B= \{5,6,7\}\\\\
  f) A^C \cap B^C\\
  \quadd A^C \cap B^C= \{0,8,9,10\}
\end{align*}
\\\\
\textbf{Problen 2.2.29}\\
A coin is tossed four times and the resulting sequence of heads and. or tails is recorded Define the events A,B,and C as follows:
\begin{align*}
  \text{A:Exactly two heads appear}\\
  \text{B: heads and tails alternate}\\
  \text{C: first two tosses are heads}\\
\end{align*}
\begin{align*}
  \textbf{a) Which two events are disjoint?:}\text{ B and C}\\
  \textbf{b) Which events are subsets} A \subseteq B.
\end{align*}
\\\\
\end{document}
